Follow-up Samples

### 2017-03-24 submission/manuscript_outline_20161024.Rmd
wrapping up mansucript text

***Carcinoma Model***
The range of model AUC's from 100 runs of 20 repeated 10 fold cross-validation was *from to this* with the AUC of the model used being *AUC value* [Figure S2C].  Interestingly, the AUCs improved from adenoma to SRN to carcinoma [Figure 2].  There was a total of *blank* OTUs in the carinoma model [Figure S3C].  Similar to the adenoma and SRN models the vast majority of OTUs classified to bacteria typically thought of as commensal but OTUs that also classified to *Fusobacterium*, *Porphyromonas*, and *Parvimonas* appear to be important for carcinoma classification [Figure S3C].  Also similar to the adenoma and SRN models there was a significant difference between the actual and model predicted group stratification calls *(P-value)*.  There was a significant decrease in the positive probability of carcinoma between initial and follow up samples *(P_value)* [Figure 2C]; suggesting that the carcinoma samples changed towards normal after treatment, unlike either adenoma or SRN.

@@

#Need to make a table with the adenoma results

@@

**Figure 1: General Differences between the Adenoma and Carcinoma Group.**  A) A significant difference was found between the adenoma and carcinoma group for thetayc (P-value = `r format(change_summary['thetayc', 'Pvalue'], scientific = FALSE, digits = 3)`).  Advanced adenomas are denoted as Screen Relevant Neoplasia (SRN).  B) NMDS of the initial and follow up samples for the adenoma group.  C) NMDS of the initial and follow up samples for the carcinoma group.

**Figure 2: The Lesion Model.** A) ROC curve: The shaded areas represent the range of values of a 100 different 80/20 splits of the test set data and the blue line represents the model using 100% of the data set and what was used for subsequent classification.  B) Summary of Important Variables.  MDA of the most important variables in the lesion model.  The black point represents the mean and the different colors are the values of each different run up to 100. C) Positive probability change from initial to follow up sample in those with carcinoma.  D) Positive probability change from initial to follow up sample if those with adenoma or advanced adenoma (Screen Relevant Neoplasia (SRN)).

**Figure 3: The Treatment Model.**  A) ROC curve: The shaded areas represent the range of values of a 100 different 80/20 splits of the test set data and the blue line represents the model using 100% of the data set and what was used for subsequent classification.  B) Summary of Important Variables.  MDA of the most important variables in the initial sample model.  The black point represents the mean and the different colors are the values of each different run up to 100.  C) Positive probability change from initial to follow up sample in those with carcinoma.  D) Positive probability change from initial to follow up sample of those with adenoma or advanced adenoma (Screen Relevant Neoplasia (SRN)).

**Figure 4: Chemotherapy and Radiation Therapy Effects on Community.**  A) Treatment model initial sample positive probability reduction for chemotherapy.  B) Treatment model initial sample positive probability reduction for radiation therapy.  C) Common OTUs based on whether chemotherapy was received or not.  The * denotes a P-value < 0.05 after multiple comparison correction.  D) Common OTUs based on whether radiation therapy was received or not.

@@

**Figure S1: Distribution of P-values from Paired Wilcoxson Analysis of All OTUs for Initial versus Follow Up**

**Figure S2: Previously Associated CRC Bacteria in Initial and Follow Up Samples.**  A) Carcinoma initial and follow up samples had an observed significant difference in initial and follow up sample for the OTUs classified as *Parvimonas* (P-value = `r format(main_crc_bugs_summary["parv", "crc_BH"], digits = 3)`), *Porphyromonas* (P-value = `r format(main_crc_bugs_summary["porp", "crc_BH"], digits = 3)`), *Peptostreptococcus* (P-value = `r format(main_crc_bugs_summary["pept", "crc_BH"], digits = 3)`).  B) Adenoma initial and follow up samples.  There were no significant differences between initial and follow up (P-value = `r format(main_crc_bugs_summary["porp", "adn_BH"], digits = 3)`.

>>>>

***Carcinoma Model***
The range of model AUC's from 100 runs of 20 repeated 10 fold cross-validation was *from to this* with the AUC of the model used being *AUC value* [Figure S2C].  Interestingly, the AUCs improved from adenoma to SRN to carcinoma [Figure 2].  There was a total of *blank* OTUs in the carinoma model [Figure S3C].  Similar to the adenoma and SRN models the vast majority of OTUs classified to bacteria typically thought of as commensal but OTUs that also classified to *Fusobacterium*, *Porphyromonas*, and *Parvimonas* appear to be important for carcinoma classification [Figure S3C].  Also similar to the adenoma and SRN models there was a significant difference between the actual and model predicted group stratification calls *(P-value)*.  There was a significant decrease in the positive probability of carcinoma between initial and follow up samples *(P_value)* [Figure 2C]; suggesting that the carcinoma samples changed towards normal after treatment, unlike either adenoma or SRN.  The one indivdiual still positive for carcinoma after treatment had an increase in carcinoma positive proability on follow up [Figure 2C].

@@

@@

**Figure 1: General Differences between Adenoma, SRN, and Carcinoma Groups After Treatment.**  A) A significant difference was found between the adenoma and carcinoma group for thetayc (P-value = `r format(change_summary['thetayc', 'Pvalue'], scientific = FALSE, digits = 3)`).  Advanced adenomas are denoted as Screen Relevant Neoplasia (SRN).  B) NMDS of the initial and follow up samples for the adenoma group.  C) NMDS of the initial and follow up samples for the carcinoma group.

**Figure 2: Treatment Response Based on Models Built for Adenoma, SRN, or Carcinoma.** A) Positive probability change from initial to follow up sample in those with adenoma.  B) Positive probability change from initial to follow up sample in those with SRN. C) Positive probability change from initial to follow up sample in those with carcinoma..

**Figure 3: The Treatment Model.**  B)   C) Positive probability change from initial to follow up sample in those with carcinoma.  D) Positive probability change from initial to follow up sample of those with adenoma or advanced adenoma (Screen Relevant Neoplasia (SRN)).

@@

**Table 1: Demographic Data of Training Cohort**

**Table 2: Demographic Data of Pre and Post Treatment Cohort**

**Figure S1: Distribution of P-values from Paired Wilcoxson Analysis of All OTUs Before and After Treatment**

**Figure S2: ROC Curves of the Adenoma, SRN, and Carcinoma Models.**  A) Adenoma ROC curve: The light greenshaded areas represent the range of values of a 100 different 80/20 splits of the test set data and the dark green line represents the model using 100% of the data set and what was used for subsequent classification.  B) SRN ROC curve: The light yellow shaded areas represent the range of values of a 100 different 80/20 splits of the test set data and the dark yellow line represents the model using 100% of the data set and what was used for subsequent classification.  C) Carcinoma ROC curve: The light red shaded areas represent the range of values of a 100 different 80/20 splits of the test set data and the dark red line represents the model using 100% of the data set and what was used for subsequent classification.

**Figure S3: Summary of Important Variables for the Adenoma, SRN, and Carcinoma Models.**  A) MDA of the most important variables in the adenoma model.  The dark green point represents the mean and the lighter green points are the value of each of the 100 different runs.  B) Summary of Important Variables in the SRN model.  MDA of the most important variables in the SRN model.  The dark yellow point represents the mean and the lighter yellow points are the value of each of the 100 different runs.  C) MDA of the most important variables in the carcinoma model.  The dark red point represents the mean and the lighter redpoints are the value of each of the 100 different runs.
